\documentclass[11pt,a4paper,sans,colorlinks,linkcolor=blue,urlcolor=blue]{moderncv}       

% possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{classic}
% style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{black}

\usepackage[utf8]{inputenc}   
\usepackage{changepage}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{changepage}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage[multiple]{footmisc}
\usepackage[T1]{fontenc}


\newlength{\mylen}
\setbox1=\hbox{$\bullet$}\setbox2=\hbox{\tiny$\bullet$}
\setlength{\mylen}{\dimexpr0.5\ht1-0.5\ht2}

\usepackage[scale=0.90]{geometry}

\address{}{Gothenburg, Sweden}{}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{+4670~172~62~75} % optional, remove / comment the line if not wanted
\email{pihl.jacob@gmail.com}

\extrainfo{
    \homepagesymbol\httplink{https://www.linkedin.com/in/jacob-pihl-3ba72a141/}
}

\name{Jacob}{Pihl}

\pagestyle{fancy}
\fancyhf{}
\lhead{\nouppercase{\rightmark} (\nouppercase{\leftmark})}
\rhead{}
\lhead{}
\rfoot{}
\lfoot{}

\begin{document}

%\begin{CJK*}{UTF8}{gbsn}    % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle
\setlength{\parskip}{0.15em}
\vspace{-40.0pt}
%\section{Objective}
%I strive to work in a fast changing and challenging working environment where i can use and increase my skills. I possess a wide knowledge in fleet management systems that could help to improve available products and let me grow with the company and drive the business into success.

\section{Work Experience}
\cventry{Aug 2020 -- Present}{Systems Developer}{Swegon}{Gothenburg}{}
{\begin{itemize}
    \itemsep0.3em
    \setlength{\itemindent}{.25in}
    \item \textbf{Jun 2021 - Present}: Part of the core developer team for Swegons new Blazor-based design tool meant to replace the old legacy one. Helped develop the new tool from scratch all the way to official release. (Blazor, .Net, Web, Azure)
    \item \textbf{Aug 2020 - May 2021}: Worked on Swegons now-legacy React-based HVAC design tool. Optimized and improved performance of the app, making it ~10x faster than previously. (Web, React, Typescript)
\end{itemize}}

\cventry{Aug 2019 -- Jun 2020}{Systems Developer}{Diadrom}{Gothenburg}{}
{\begin{itemize}
    \itemsep0.3em
    \setlength{\itemindent}{.25in}
    \item \textbf{Aug 2019 - Mar 2020}: Front end developer consultant at Volvo IT. Developing a multi-platform diagnostics application for trucks using web technologies. Agile workflow with DevOps was used for continuous integration and deployment. (Web, TypeScript, Polymer)
\end{itemize}}

\cventry{Mar 2015 -- May 2017}{Programming Teacher}{Halmstad City \& Halmstad University}{Halmstad}{}
{\begin{itemize}
    \itemsep0.3em
    \setlength{\itemindent}{.25in}
    \item Taught kids and adults how to program using Scratch in cooperation with Halmstad City.
\end{itemize}}

\cventry{Sep 2015 -- Nov 2015}
{Programming in Java T.A}{Halmstad University}{Halmstad}{}
{\begin{itemize}
    \itemsep0.3em
    \setlength{\itemindent}{.25in}
    \item Teaching assistant during computer labs in the Programming in Java course.
\end{itemize}}


%%%% PROJECTS %%%%
\section{Personal Projects}
\cventry{Contributor}{TabBlazor}{\httplink{http://tabblazor.com}}{Sweden}{}
{\begin{itemize}
    \itemsep0.3em
    \setlength{\itemindent}{.25in}
    \item Helped with major contributions to TabBlazor, an open source component library for Blazor. (Blazor, .Net, Web)
\end{itemize}}

\cventry{Creator}{Web-based sauna booking tool}{Independent}{Sweden}{}
{\begin{itemize}
    \itemsep0.3em
    \setlength{\itemindent}{.25in}
    \item Created a web-based booking tool for the community sauna at my parent's summer house. Used Trello for organization. (Web, Python, SQL)
\end{itemize}}

%%%% EDUCATION %%%%%
\section{Education}
\cventry{2017--2019}{Master of Science in Engineering, Computer Science \& Engineering}{Halmstad University}{Sweden}{}
{\begin{itemize}
    \setlength{\itemindent}{.25in}
    \itemsep0.3em
    \item \textit{\textbf{Thesis:}} Robotic exercise coach using Deep Learning technologies and machine learning. (Python, Tensorflow, ROS)
\end{itemize}}

\cventry{Feb 2018 -- Jul 2018}{Exchange Student MSc Computer Science \& Engineering}{Taiwan National University of Science and Technology}{Taiwan}{87/100 GPA}{}

\cventry{Sep 2017 -- Jan 2018}{Exchange Student BSc Computer Science \& Engineering}{Korea University}{South Korea}{80.5/100 GPA}{}

\cventry{2014 -- 2017}{BSc with a major in Computer Science \& Engineering}{Halmstad University}{Sweden}{}
{\begin{itemize}
    \setlength{\itemindent}{.25in}
    \itemsep0.3em
    \item \textit{\textbf{Thesis:}} Comparison of Computer Vision Algorithms. (Python, OpenCV, MATLAB)
\end{itemize}}

\section{Other}
Speaks Swedish, English and intermediate Mandarin Chinese.
\\
{Main Programming/Scripting Languages (Intermediate 1-3 years): \textbf{\textit{C\# .Net, TypeScript}}}
\\
Publications: \href{https://arxiv.org/abs/1909.12262}{\textbf{\textsc{Exercising with an "Iron Man"}}}

\section{References}
Portfolio: \href{https://github.com/jacobpihl}{\textbf{\textsc{GitHub}}}
\\
Work: \href{https://www.linkedin.com/in/jacob-pihl-3ba72a141/}{\textbf{LinkedIn}}

\end{document}
%% end of file `cv.tex'.