\documentclass[a4paper]{twentysecondcv} % a4paper or latterpaper
\usepackage{anyfontsize}
\usepackage{titlesec}

\usepackage[most]{tcolorbox}
\newtcbox{\badge}[1][blue]{
  on line, 
  arc=2pt,
  colback=#1!50!black,
  colframe=#1!50!black,
  fontupper=\color{white},
  boxrule=1pt, 
  boxsep=0pt,
  left=6pt,
  right=6pt,
  top=2pt,
  bottom=2pt
}

\setcounter{secnumdepth}{0}
\titleformat{\section}{\LARGE}{\rlap{\color{white}\rule[-0.4cm]{\linewidth}{.5cm}} \thesection}{0.5em}{}
%-------------
%	 PERSONAL INFORMATION
%-------------

\profilepic{} % Profile picture

\cvname{Jacob Pihl} % Your name
\cvjobtitle{Software Developer} % Job title/career

\cvdate{} % Date of birth
\cvaddress{Gothenburg} % Short address/location
\cvnumberphone{+46 701 72 62 75} % Phone number
\cvsite{} % Personal website
\cvmail{pihl.jacob@gmail.com} % Email address
\cvlinkedin{jacob-pihl-3ba72a141} % Linkedin user account
\cvgithub{jacobpihl}

%-------------

\begin{document}

%-------------
%  INTRO
%-------------

% \intro{Welcome to my CV!\\I'm happy you found your way here!}

%-------------
%  PROFILE
%-------------

\profile{About me}
{\hspace{1em}
I'm an exploring individual who likes sailing and try my best to stay active. Always eager to try new things and thrive in dynamic environments where there is lots of change and growth.

Professionally I value progress and usually feel the most fulfilled when I'm actively involved in exciting projects and challenges. Preferably with an opportunity to expand my understanding along the way.
}

%-------------
%  ABOUT ME
%-------------

\aboutme{Education}{
B.Sc. \& M.Sc. in Computer Science \& Engineering from Halmstad University
}

%-------------
%  INTERESTS
%-------------

\interest{Language}{
Swedish - Native \\
English - Professional Proficiency \\
Mandarin Chinese - Moderate
}

%-------------
%    TAGS
%-------------

\tags{Tags}
{
\badge{dotnet}      \badge{C\#}         \badge{Blazor}
\badge{Azure}       \badge{RabbitMQ}    \badge{CQRS}
\badge{Terraform}   \badge{GraphQL}     \badge{React}
\badge{Docker}      \badge{Linode}      \badge{Docker Compose}
\badge{Git}         \badge{NextJs}      \badge{Vercel}
\badge{Cosmos DB}   \badge{Traefik}     \badge{Flutter}
\badge{Postgres}    \badge{SQL}         \badge{NoSQL}
\badge{Redux}       \badge{Typescript}  \badge{CSS}
\badge{DevOps}      \badge{CI/CD}       \badge{Redis}
}

\makeprofile % Print the sidebar

%-------------
%  EXPERIENCE
%-------------

\section{Work Experience}
\begin{twenty} % Environment for a list with descriptions
    \twentyitemtime
    {mainblue}{white}
    {Aug 2020}{Present}
    {Swegon}
    {Gothenburg}
    {
    \\
    \textbf{Fullstack/Lead developer \& DevOps}
    \\
    \textit{Oct 2024 - Present}
    \\
    Worked on Swegons new solution for partner companies, allowing them to buy and sell Swegons products in an Ecom-like fashion. Communicated with stakeholders \& other relevant people to determine requirements and scope for this new solution. Used Microsoft based stack. (dotnet, Blazor, Azure, GraphQL, MSSQL)

    \vspace{1em}
    
    \textbf{Fullstack/Lead developer \& DevOps}
    \\
    \textit{Mar 2024 - Oct 2024}
    \\
    Re-developed Swegon's \href{https://sweflow.swegon.com/}{Sweflow} app as a traditional web-app with a frontend (React) and a backend (dotnet), both deployed via Azure using Terraform.
    
    Created a process and a tool to migrate all commissioned Swegon "Wise" systems from the deprecated "Wise" system designer to the brand new one.

    \vspace{1em}

    \textbf{Fullstack/Lead developer \& DevOps}
    \\
    \textit{Jun 2021 - Mar 2024}
    \\
    Worked with UI/UX designers, product specialists and 2 development teams to create Swegons new "Wise" systems designer. Coordinated and collaborated with different teams to ensure feature parity with the old software and to develop brand new features. Mentored and taught a student in the team. Used Microsoft based stack with CQRS. (dotnet, Blazor, Azure, RabbitMQ, Terraform)
    
    \vspace{1em}
    
    \textbf{Front-end developer}
    \\
    \textit{Aug 2020 - May 2021}
    \\
    Maintained and improved Swegons legacy product picker \& simulator software.
    Worked on improvements to the applications performance bringing it from completely unusable to a decent user experience in some scenarios.
    Used React based stack. (React, Redux, Typescript)
    }
    
    \vspace{.5em}
    
    \twentyitemtime
    {mainblue}{mainblue}
    {Aug 2019}{Jun 2020}
    {Diadrom}
    {Gothenburg}
    {Front end focused developer consultant at Volvo IT. \\
    Worked on a multi-platform diagnostics application for trucks using web tech. (TypeScript, Polymer)}
    
    \\
    
    % \twentyitem
    % {2016-2019}
    % {Software Developer (Part-time)}
    % {Upwork}
    % {Remote consulting \& web development for various companies and people through Upwork. (Web technologies)}
    
    % \twentyitem
    % {2015-2017}
    % {Programming Teacher}
    % {Halmstad University, Halmstad}
    % {Taught kids and adults how to program using Scratch in cooperation with Halmstad City.}
\end{twenty}

%-------------
%  OWN PROJECTS
%-------------

\section{Personal Projects}
\begin{twenty}
    \twentyitem
    {Co-Maintainer}
    {TabBlazor}
    {\href{http://tabblazor.com}{tabblazor.com}}
    {Co-maintainer \& developer for TabBlazor, an open source component library for Blazor.}
\end{twenty}

\begin{twenty}
    \twentyitem
    {Developer}
    {BankId Clone}
    {}
    {Developed a clone of the Swedish BankID app and system using dotnet, Flutter, Docker, Traefik, RabbitMq. Deployment to Linode and Vercel using Github Actions}
\end{twenty}

%-------------
%  EDUCATION
%-------------

% \section{Education}
% \begin{twenty} % Environment for a list with descriptions
%     \twentyitemtime
%     {mainblue}{mainblue}
%     {Sep 2017}{Jun 2019}
%     {M.Sc. Computer Science \& Engineering}
%     {Halmstad University}
%     {Masters degree with exchange semesters to South Korea \& Taiwan}
%     % {\begin{itemize}
%     %     \setlength\itemsep{.5em}
%     %     \item {
%     %         \textbf{Aug 2018 - Jun 2019}\\
%     %         Thesis work at Halmstad University, Sweden\\
%     %         \href
%     %         {https://ieeexplore.ieee.org/abstract/document/9223552}
%     %         {Exercising with an "Iron Man"}
%     %     }
%     %     \item {\textbf{Feb 2018 - Jul 2018}\\Exchange student at NTUST, Taipei, Taiwan (R.O.C)}
%     %     \item {\textbf{Sep 2017 - Jan 2018}\\Exchange student at Korea University, Seoul, South Korea}
%     % \end{itemize}}
    
%     \\
    
%     \twentyitem
%     {2014-2017}
%     {B.Sc. in Computer Science \& Engineering}
%     {Halmstad University}
%     {Bachelors degree}
%     % {\makeList{
%     %     \textit{Thesis:} Comparison of Computer Vision Algorithms
%     % }}
% \end{twenty}

\end{document} 